Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}

### 2017-03-08 ident_manu.Rnw
fixed theme issues in figures

p <- ggplot(toplo_all, aes(y = Parameter, x = L1, fill = Sensitivity)) + 
  geom_tile(colour = 'black') + 
  pbase +
  scale_y_discrete('Parameter', 
    expand = c(0, 0),
    breaks = toplo_all$Parameter, 
    labels = parse(text = toplo_all$Parameter)
    ) + 
  scale_x_discrete('State variable', expand = c(0, 0)) +
  scale_fill_distiller(palette = "Spectral", trans = 'log10',  na.value = 'grey95') +
  facet_grid(Category~., scales = 'free_y', space = 'free') + 
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 10))

@@

cols <- RColorBrewer::brewer.pal(11, 'Spectral')
lncol <- 'darkgrey'
sz <- 2

p1 <- ggplot(toplo, aes(x = N, group = N)) + 
  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = lncol) + 
  geom_point(aes(y = ave, shape = 'Ave'), fill = cols[5], colour = lncol, size = sz) + 
  geom_point(aes(y = med, shape = 'Med'), fill = cols[3], colour = lncol, size = sz) + 
  scale_shape_manual(values = c(21, 24)) + 
  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
  mytheme +
  theme(legend.position = 'none') + 
  ggtitle('(a) By parameter category')

@@

p2 <- ggplot(toplo2, aes(x = N, group = N)) + 
  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = lncol) + 
  geom_point(aes(y = ave, shape = 'Ave', fill = 'Ave'), colour = lncol, size = sz) + 
  geom_point(aes(y = med, shape = 'Med', fill = 'Med'), colour = lncol, size = sz) + 
  scale_shape_manual(name = '', labels = c('Ave', 'Med'), values = c(21, 24)) + 
  scale_fill_manual(name = '', labels = c('Ave', 'Med'), values = cols[c(5, 3)]) +
  facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
  mytheme + 
  theme(legend.title = element_blank()) + 
  ggtitle('(b) By top parameters, all categories')

pleg <- g_legend(p2)
p2 <- p2 + theme(legend.position = 'none')

@@

p1 <- ggplot(toplo, aes(x = N, group = N)) + 
  geom_line(aes(y = ave, group = `State variable`), colour = lncol) + 
  geom_point(aes(y = ave, fill = `State variable`), shape = 21, colour = lncol, 
    size = sz
    ) + 
  fils + 
  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
  mytheme +
  scale_y_continuous(trans = 'log10') + 
  theme(legend.position = 'none') + 
  ggtitle('(a) By parameter category')

@@

pleg <- g_legend(p2)
p2 <- p2 + theme(legend.position = 'none')

@@

ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line() + 
  geom_text_repel(aes(label = Parameter), size = 3,
    parse = TRUE,
    point.padding = unit(0, "lines"),
    box.padding = unit(1, "lines"), 
    force = 3
    ) +
  geom_point(aes(fill = Category), shape = 21, size = 4) +
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  facet_wrap(~L1, scales= 'free', ncol = 4) + 
  scale_y_continuous('Identifiability') + 
  scale_x_continuous(
    'Parameters selected by sensitivity',
    breaks = toplo$Selected, 
    expand = c(.1, .1)
    ) + 
  cols +
  pthm +
  theme(legend.position = 'top')

>>>>

p <- ggplot(toplo_all, aes(y = Parameter, x = L1, fill = Sensitivity)) + 
  geom_tile(colour = 'black') + 
  pbase +
  scale_y_discrete('Parameter', 
    expand = c(0, 0),
    breaks = toplo_all$Parameter, 
    labels = parse(text = toplo_all$Parameter)
    ) + 
  scale_x_discrete('State variable', expand = c(0, 0)) +
  scale_fill_distiller(palette = "Spectral", trans = 'log10',  na.value = 'grey95') +
  facet_grid(Category~., scales = 'free_y', space = 'free') + 
  guides(fill = guide_colourbar(barheight = 0.25, barwidth = 5, label.theme = element_text(size = 6, angle = 0)))

@@

cols <- RColorBrewer::brewer.pal(11, 'Spectral')
lncol <- 'darkgrey'
sz <- 3

p1 <- ggplot(toplo, aes(x = N, group = N)) + 
  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = lncol) + 
  geom_point(aes(y = ave, shape = 'Ave'), fill = cols[5], colour = lncol, size = sz) + 
  geom_point(aes(y = med, shape = 'Med'), fill = cols[3], colour = lncol, size = sz) + 
  scale_shape_manual(values = c(21, 24)) + 
  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
  mytheme %+replace%
  theme(legend.position = 'none') + 
  ggtitle('(a) By parameter category')

@@

p2 <- ggplot(toplo2, aes(x = N, group = N)) + 
  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = lncol) + 
  geom_point(aes(y = ave, shape = 'Ave', fill = 'Ave'), colour = lncol, size = sz) + 
  geom_point(aes(y = med, shape = 'Med', fill = 'Med'), colour = lncol, size = sz) + 
  scale_shape_manual(name = '', labels = c('Ave', 'Med'), values = c(21, 24)) + 
  scale_fill_manual(name = '', labels = c('Ave', 'Med'), values = cols[c(5, 3)]) +
  facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
  mytheme %+replace%
  theme(legend.title = element_blank()) + 
  ggtitle('(b) By top parameters, all categories')

pleg <- g_legend(p2)
p2 <- p2 + 
  mytheme %+replace%
  theme(legend.position = 'none')

@@

p1 <- ggplot(toplo, aes(x = N, group = N)) + 
  geom_line(aes(y = ave, group = `State variable`), colour = lncol) + 
  geom_point(aes(y = ave, fill = `State variable`), shape = 21, colour = lncol, 
    size = sz
    ) + 
  fils + 
  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
  mytheme %+replace%
  theme(legend.position = 'none') + 
  scale_y_continuous(trans = 'log10') + 
  ggtitle('(a) By parameter category')

@@

pleg <- g_legend(p2)
p2 <- p2 +
  mytheme %+replace%
  theme(legend.position = 'none')

@@

ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line() + 
  geom_text_repel(aes(label = Parameter), size = 3,
    parse = TRUE,
    point.padding = unit(0, "lines"),
    box.padding = unit(1, "lines"), 
    force = 3
    ) +
  geom_point(aes(fill = Category), shape = 21, size = 4) +
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  facet_wrap(~L1, scales= 'free', ncol = 4) + 
  scale_y_continuous('Identifiability') + 
  scale_x_continuous(
    'Parameters selected by sensitivity',
    breaks = toplo$Selected, 
    expand = c(.1, .1)
    ) + 
  cols +
  pthm %+replace%
  theme(legend.position = 'top')

### 2017-03-08 ident_manu.tex
fixed theme issues in figures

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Mon Mar 6 11:12:53 2017 -0600, \href{https://github.com/fawda123/identifiability/commit/4a06dbf55054203e59978de8be41053a6c7b9ba1}{4a06dbf55054203e59978de8be41053a6c7b9ba1}}

>>>>

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Tue Mar 7 16:55:36 2017 -0600, \href{https://github.com/fawda123/identifiability/commit/8f38d5a2d17442eb0f3f3d4db61d379b841c8830}{8f38d5a2d17442eb0f3f3d4db61d379b841c8830}}
